\documentclass[12pt]{fithesis2}

% ===== LOADING PACKAGES =====
% language settings, main documnet language last
\usepackage[english]{babel}
% enabling new fonts support (nicer)
\usepackage{lmodern}
% setting input encoding
\usepackage[utf8]{inputenc}
% setting output encoding
\usepackage[T1]{fontenc}
% fithesis2 requires csquotes
\usepackage{csquotes}

\usepackage[
    backend=biber,      % use biber as backend instead of BiBTeX
    style=alphabetic,   % citation style
	url=true,           % display urls in bibliography
	hyperref=auto,      % detect hyperref and create links
    firstinits=true,    % abbreviate first names to initials
    maxbibnames=5,      % maxiumim number of authors before making 'et al.'
    alldates=iso8601,   % set date format to ISO 8601
]{biblatex}
\addbibresource{thesis.bib}
% setting custom colors for l

% FI THESIS settings
\thesistitle{Something with BCS}
\thesissubtitle{Master thesis}
\thesisstudent{Matej Troják}
\thesiswoman{false}
\thesisfaculty{fi}
\thesisyear{autumn 2017}
\thesisadvisor{RNDr.\ David Šafránek,\ Ph.D.}
\thesislang{en}

% ===== BEGIN DOCUMENT =====
\begin{document}

\FrontMatter
\ThesisTitlePage

\begin{ThesisDeclaration}
\DeclarationText
\AdvisorName
\end{ThesisDeclaration}

\begin{ThesisThanks}
Many thanks to you all.

\vspace{1em}
\noindent
There would be much less
algebra,        % advancements, art, adrenaline, archery, astrophotography, algebra
board gaming,   % beauty, baking, beer, board gaming
curiosity,      % courage, contemplation, cooking, cakes, curiosity
drama,          % discipline, devotion, drama
experience,     % empathy, experience
functional programmig,  % fun, friendliness, faith, functional programmig
geekiness,      % GEB, good books, geekiness
honesty,        % humour, honesty
inspiration,    % improvements, ideas, idealisms, inspiration
joy,            % jokes, joy
knowledge,      % knowledge
learning,       % learning, love
magic,          % meaning, magic, miracles, meta, moose
nighttime walks,    % nighttime walks, Norway
OpenLabs,       % organization, openness, optimism, OpenLabs
puzzle hunts,   % peace, patience, procrastination, puzzle hunts
quiet,          % quiet
respect,        % research, respect
surprises,      % spontaneity, silence, security, stories, star gazing, surprises
trust,          % typographic correctness, tolerance, trust
unpredictability,   % understanding, unity, unpredictability
vigilance,      % vigilance
Wachumba,       % wisdom, Wachumba
xylophone,      % xylophone
yummies         % yellow, you, yummies
and
zeal            % Zendo, Zen, zeal
in the world for me without you.

\vspace{0.65\textheight}
\noindent
Access to computing and storage facilities owned by parties and projects contributing to the National Grid Infrastructure MetaCentrum, provided under the programme Projects of Large Infrastructure for Research, Development, and Innovations(LM2010005), is greatly appreciated.
\end{ThesisThanks}

\begin{ThesisAbstract}
This thesis explores the randomness of outputs created by authenticated encryption schemes submitted to the  competition. Tested scenarios included three different modes of public message numbers. For the assessment, four different software tools were used: three common statistical batteries and a novel genetically inspired framework. The obtained results are interpreted in two ways: Firstly, to gain insights into the quality of the proposed  candidates. Secondly, to compare and contrast the used randomness testing tools. Directions for future research are proposed based on the obtained conclusions.
\end{ThesisAbstract}

\begin{ThesisKeyWords}
statistical randomness, authenticated encryption, CAESAR, evolutionary algorithms, genetic programming
\end{ThesisKeyWords}

\MainMatter
\tableofcontents

\chapter{First one}

here we go

\printbibliography

\end{document}
